\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{tcolorbox}
\usepackage{pgfplots}
\usepackage{xcolor}
\geometry{top=1in, bottom=1in, left=1in, right=1in}

\pagestyle{empty}

\newcommand{\progressbar}[2]{%
    \begin{tcolorbox}[width=\linewidth, colback=gray!0, colframe=white, arc=3mm, boxrule=0pt, left=2pt, right=2pt, top=2pt, bottom=2pt]
        \textbf{#1} \\
        \begin{tikzpicture}
            \draw[fill=black!70] (0,0) rectangle (#2,0.3);
            \draw[draw=black] (0,0) rectangle (5,0.3);
        \end{tikzpicture}
    \end{tcolorbox}
}

\begin{document}

\begin{center}
    \textbf{\huge TOUHIDUL ISLAM SAAD}\\
    \textsc{Data Analyst | Full-Stack Developer | Computer Vision Researcher} \\
    \href{mailto:pro.saaad@gmail.com}{pro.saaad@gmail.com} | 
    \href{https://linkedin.com/in/saadsaadsaad/}{{LinkedIn}} |
    +8801828327033 | 
    \href{https://wa.me/+8801828327033}{WhatsApp} | Dhaka, Bangladesh 
\end{center}

\noindent
\rule{\linewidth}{0.5mm}

\section*{ABOUT ME}
To leverage my expertise in data analysis, deep learning, and full-stack development using Node.js (NextJS, NestJS, Express.js) for 3 years, along with proficiency in Tailwind UI, ReactJS, PostgreSQL, MongoDB, and image segmentation research.

\section*{CERTIFICATION}
\textbf{IEEE Student Professional Awareness Venture (SPAVe) 6.0} | March 16th, 2023 \\
Participant \\
Certified by IEEE AIUB Student Branch

\section*{EDUCATION}
\textbf{Bachelor of Science in Computer Science Engineering} \\
American International University-Bangladesh (\href{https://www.aiub.edu/}{\textit{AIUB}}) \\
January 2022 - January 2025

\section*{LANGUAGES}
\progressbar{Bangla}{5} 
\progressbar{English}{4} 
\progressbar{Française \href{https://www.afdhaka.org/}{[\textit{Alliance Française de Dhaka}]}}{3} 


\section*{WORK EXPERIENCE}

\textbf{Hands-on practice} 
\vspace{0.3cm}

\begin{itemize}

    \item \texttt{MERN Backend} \hfill \texttt{7-8 January 2025}  
    \begin{itemize}
        \item Built with Express JS, TypeScript, and MongoDB.
        \item Implemented functionality to add a product with attributes: Name, Description, Price, Discount, Image URL, Availability, Unique product code.
        \item Auto-generated a unique code based on the product name by: Extracting the longest strictly increasing substring, Applying specific formatting.
        \item Ensured each product is linked to a valid category with validation for consistency.
        \item Enabled product updates, including: Status, Description, Discount and implemented filtering by: Category, Name, Pricing calculation with discount details.
    \end{itemize}
    
    \hfill \href{https://github.com/0Sa-ad0/backend-challenge}{\textit{Github Link}}  
    \vspace{0.3cm}

    \item \texttt{Data Analysis} \hfill \texttt{August - September 2024}  
    \begin{itemize}[label=--]  % Double dash for better visibility
        \item Analyzed the dataset with 768 entries.
        \item Handled missing values by filling them with zeros.
        \item Applied Naive Bayes algorithm for classification, predicting whether a patient has diabetes based on medical metrics.
        \item Achieved an accuracy of 78 percent, with a confusion matrix showing true positives, true negatives, false positives, and false negatives.
    \end{itemize} 

    \hfill \href{https://github.com/0Sa-ad0/Data-mining}{\textit{Github Link}}  
    \vspace{0.3cm}

    \item \texttt{NextJS} \hfill \texttt{April - May 2024}  
    \begin{itemize}[label=--]
        \item AXIOS for making HTTP requests (API calls in NestJS).
        \item React core principles including Props, States, and Hooks.
        \item Next.js features such as routing, rendering, and libraries.
        \item Custom form validation using Vanilla JavaScript (without relying on HTML validation).
        \item Tailwind UI for styling.
        \item Authentication implementation.
    \end{itemize}

    \hfill \href{https://github.com/0Sa-ad0/advanced-web-tech/tree/main/NextJS}{\textit{Github Link}} 
    \vspace{0.3cm}

    \item \texttt{NestJS} \hfill \texttt{February - March 2024}  
    \begin{itemize}[label=--]
        \item 15 APIs with comprehensive Controller and Service layers.
        \item Pipes for data transformation and validation.
        \item File upload functionality.
        \item Database relationships, including One-to-One and One-to-Many associations and query optimization.
        \item JWT, OAuth authentication alongside Bcrypt for password hashing and session management.
        \item Email functionality using the Mailer module with SMTP integration.
    \end{itemize} 

    \hfill \href{https://github.com/0Sa-ad0/advanced-web-tech/tree/main/NestJS}{\textit{Github Link}}  
    \vspace{0.3cm}

    \item \texttt{Web technologies} \hfill \texttt{October - December 2023}  
    \begin{itemize}[label=--]
        \item Developed using HTML, PHP, CSS, JavaScript, and Ajax, managed via XAMPP.
        
        \item Admin Features: Manage drivers, admins, earnings, locations, riders, and user route bookings.
    
        \item Customer Support Manager Features: Dashboard with trip summaries, history, driver earnings, reported issues, trip ratings, and feedback.
    
        \item Driver Features: Dashboard for profile management, license verification, support, responses, and ride requests.
    
        \item Rider Features: Ride tracking, trip history, cancellation, multiple payment options, emergency services, and ride scheduling.
        
    \end{itemize}

    \hfill \href{https://github.com/0Sa-ad0/web-tech}{\textit{Github Link}}

\end{itemize}

\section*{CORE SKILLS}
\begin{itemize}[label=-]
    \item \textbf{Primary Programming Languages:} Python, JavaScript
    \item \textbf{Other Programming Languages:} C++ (OpenGL), Java, C\#, R, HTML5, CSS3, PHP, Tailwind CSS, ReactJS
    \item \textbf{Advanced Database Management:} PostgreSQL, MongoDB, MySQL, Microsoft SQL Server (T-SQL, complex queries, stored procedures)
    \item \textbf{Visual Development:} Figma, Droip
    \item \textbf{API Development \& Integration:} Postman API, RESTful API
    \item \textbf{Version Control \& DevOps:} Git, Docker, Agile
    \item \textbf{Web \& App Development Frameworks:} Socket.IO, Redux, Bootstrap, Chrome DevTools
    \item \textbf{Software Testing \& Automation:}  
    \begin{itemize}
        \item \textbf{Test Automation Tool:} Selenium
        \item \textbf{Performance Testing:} JMeter
        \item \textbf{Bug Tracking \& Test Management:} Redmine, JIRA, TestRail
        \item \textbf{Mobile Testing:} Appium
        \item \textbf{UI/UX Testing:} SikuliX
        \item \textbf{Test Case Writing, Front-End Testing}
    \end{itemize}
    \item \textbf{Other Technical Skills:}
    \begin{itemize}
        \item Data migration and integration, Data analysis and optimization (Google Analytics)
        \item SOAP notes, Keyboard shortcuts, Web browsing, Operating remote desktop applications
        \item Typing speed: 33 WPM / 156 CPM, Accuracy: 100\%
    \end{itemize}
\end{itemize}

\section*{SOFT SKILLS}
\begin{itemize}[label=-]
        \item Communication, Adaptability, Leadership, Creativity, Time Management
        \item Attention to Detail, Cognitive Functionality, Proactive Mindset, Dynamic Thinking, Critical Issue Rationalization
        \item Client-facing Consulting Skills, Team Collaboration (Enterprise, Development, Technical Support, Product Teams), Innovation and Adaptability, Documentation and Technical Writing
\end{itemize}

\end{document}
